Pangenome graph layout by Path-Guided Stochastic Gradient Descent

### 2023-08-03 manuscript/fig_sketches.tex
fix merge conflict

\begin{figure*}[!htb]
	\centering
		%\hline
		\begin{subfigure}[t]{0.32\textwidth}
			\centering
			\caption{}
			\includegraphics[width=\linewidth]{fig/algorithm/TODO_1D_metrics_explained.pdf}
			\label{fig:1d_before_update}
		\end{subfigure}
		\begin{subfigure}[t]{0.32\textwidth}
		\centering
		\caption{}
		\includegraphics[width=\linewidth]{fig/algorithm/TODO_1D_sorting_explained.pdf}
		\label{fig:1d_before_update_highlighted}
		\end{subfigure}
		\begin{subfigure}[t]{0.32\textwidth}
		\centering
		\caption{}
		\includegraphics[width=\linewidth]{fig/algorithm/TODO_1D_sorting_explained.pdf}
		\label{fig:1d_after_update}
		\end{subfigure}	
		%\smallskip
		\begin{subfigure}[t]{0.32\textwidth}
			\centering
			\caption{}
			\includegraphics[width=\linewidth]{fig/algorithm/TODO_pg_sgd_update_sketch.png}
			\label{fig:2d_before_update}
		\end{subfigure}
		\begin{subfigure}[t]{0.32\textwidth}
			\centering
			\caption{}
			\includegraphics[width=\linewidth]{fig/algorithm/TODO_zipf_curve.jpg}
			\label{fig:2d_before_update_highlighted}
		\end{subfigure}
		\begin{subfigure}[t]{0.32\textwidth}
		\centering
		\caption{}
		\includegraphics[width=\linewidth]{fig/algorithm/TODO_zipf_curve.jpg}
		\label{fig:2d_after_update}
		\end{subfigure}	
	\caption{
		PG-SGD update operation sketches. \textbf{(a)-(c)} 1D layout sketch of an update operation moving a pair of nodes at a time. Edges are not shown. \textbf{(d)-(f)} 2D layout sketch of an update operation moving a pair of nodes at a time. Edges are drawn as black links.
		\textbf{(a)} State of the graph before the 1D update. \textbf{(b)} State of the graph before the update highlighting the discrepancy of the layout distance versus the path nucleotide distance of the blue nodes in 1D.  \textbf{(c)} State of the graph after the 1D update. \textbf{(d)} State of the graph before the 2D update. \textbf{(e)} State of the graph before the update highlighting the discrepancy of the layout distance versus the path nucleotide distance of the blue nodes in 2D. \textbf{(f)} State of the graph after the 2D update.
	}
	\label{fig:sketches}
\end{figure*}

>>>>

\begin{figure*}[!htb]
	\centering
		%\hline
		\includegraphics[width=\linewidth, trim=0cm 8cm 0cm 0cm, clip]{fig/sketches/PG-SGD.drawio.pdf}
	\caption{
		2D PG-SGD update operation sketches. \\
		\FIXME{ADD CAPTION.} \\ 
		\FIXME{PROVIDE SEVERAL NICE FIGURES SO WE CAN REARRANGE STUFF INTO SUBFIGURES.}
	}
	\label{fig:sketches}
\end{figure*}
